Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control

### 2019-06-24 NFES_Review/article.tex
article progress

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%toc: yes
%pagenum: yes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother
          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
\usepackage{etoolbox}

@@

\end{frontmatter}
\tableofcontents

@@

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a voltage power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected. Figure 6.2 describes a typical electrospinning set-up \unskip~\cite{527120:12073538}. Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}. Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}. Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control. NFES has suffered several modifications to improve the precision and accuracy of the fiber deposition.

\section{NFES}
\unskip~\cite{527120:11973130}

\unskip~\cite{527120:11974314}

\unskip~\cite{527120:11974329}

\unskip~\cite{527120:11974305}

\unskip~\cite{527120:11974306}

\unskip~\cite{527120:11974308}

\unskip~\cite{527120:11974310}

\unskip~\cite{527120:11974311}

\unskip~\cite{527120:11974312}

\unskip~\cite{527120:11974313}

\unskip~\cite{527120:11974316}

\unskip~\cite{527120:11974320}

\unskip~\cite{527120:11974321}

\unskip~\cite{527120:11974322}

\unskip~\cite{527120:11974323}

\unskip~\cite{527120:11974324}

\unskip~\cite{527120:11974325}

\unskip~\cite{527120:11974326}

\unskip~\cite{527120:11974327}

\unskip~\cite{527120:11974328}

\unskip~\cite{527120:11974304}

\unskip~\cite{527120:11974307}

\unskip~\cite{527120:12033655}

\unskip~\cite{527120:12033656}

\unskip~\cite{527120:12033657}

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

@@

@@

Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Polymer Solution and Process Parameters}

\section{Applications}

\section{Fiber Characterization}

\section{Conclusion}

\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{section}{\numberline{}\refname}}{}{}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%pagenum: yes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother

@@

\end{frontmatter}

@@

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a voltage power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected.  Figure~\ref{f-fe28447572e9} describes a typical near-field electrospinning set-up \unskip~\cite{527120:12073538}. Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning \unskip~\cite{527120:12033655}. Moreover, if the distance between the collector and the dispensing needle is greater, the configuration is known as FFES or far-field electrospinning \unskip~\cite{527120:12073581}. Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition. This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.

\bgroup
\fixFloatSize{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}{\includegraphics{images/596d6818-a246-493e-bea0-03f815ab8ff8-unfes.jpg}}{}
\makeatother 
\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130} .}}
\label{f-fe28447572e9}
\end{figure*}
\egroup

\section{Polymer Solution and NFES Parameters}
To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited. Kameoka et al (2003) demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip. Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns (Sun et al 2006). Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner. Using a spinneret with a reservoir (e.g. syringe) of solution generally produces fibers with diameter of a few micrometers [Gupta et al 2007; Xue et al 2014] since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through. Coppola et al (2014) have showned a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop,  averting the issue of nozzle clogging. The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al's (2014) work. The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al (2008) used a 100 \textmu m inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al (2013) used a \textmu m-diameter tip Tungsten spinneret in a 26 gauge needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).

\subsection{Applied Voltage}Further development in the near field electrospinning spinning process have attempted to improve fiber deposition precision and reducing fiber diameter. Camillo et al (2013) was able to fabricate 100 nm diameter fiber at an applied voltage of 1.5 kV and a tip to collector distance of 500 \textmu m using a modified fine tip spinneret. Separate reports by Chang et al (2008) and Bisht et al (2011) have shown that higher voltage leads to a significant increase in the fiber diameter (in the micrometer range) and loss of jet stability. The remedy is to significantly reduce the voltage used in the electrospinning process to about 200 to 600 V with tip to collector distance at about 0.5 to 1 mm. However, the charges on the solution drop at the tip of the needle were insufficient to break free from the surface tension to initiate electrospinning without assistance. Chang et al (2008) used a tungsten probe tip and Bisht et al (2011) used a glass microprobe tip (1 to 3 \textmu m tip diameter) to mechanically draw the solution at the tip of the needle to initiate electrospinning. In the study by Chang et al (2008), reduction of electrospinning voltage from 1.5 kV (at tip to collector distance of 500 \textmu m) to 600 V reduces the fiber diameter from 3 \textmu m to 50 nm. Using a lower voltage of 200 V with tip to collector distance of 1 mm, Bisht et al (2011) was able to pattern nanofibers (polyethylene oxide) with diameter below 20 nm. Similar to electrospinning with longer tip to collector distance, it is likely that there is an optimum voltage which the fiber diameter obtained will be at its finest. Voltage higher or lower than this value will see an increase in the fiber diameter. Song et al (2015) showed that when the voltage for electrospinning polystyrene was increased from 400 to 500V, at a tip to collector distance of 20 \textmu m, the fiber diameter reduced from close to 160 nm to about 60 nm. Such fiber diameter response to voltage is due to a balance of stretching of the jet and the speed at which it hit the collector. While increasing voltage causes greater stretching which reduces the fiber diameter, this also causes greater jet acceleration where the stretching terminates when the jet hit the collector.

To use a low working voltage in near field electrospinning while eliminating the need to use a physical object to initiate electrospinning, an alternative is to use a higher voltage for initiation of electrospinning and switch to a lower voltage once the jet has erupted from the nozzle. Huang et al (2014) used this concept with a movable stage collector to produce ordered patterns with interfiber pitch of 50 \textmu m. By controlling the height between the nozzle tip and the collector stage and the speed of stage, fibers with different orientation and cross-sectional shape can be obtained. Generally, closer distance between nozzle tip and collector (ranging from 0.5 mm to 2 mm) results in flat fibers due to impaction of the electrospinning jet. A limitation of the setup is that the landing point at electrospinning jet initiation cannot be determined although subsequent adjustment can be made after the jet has landed or the structure can be built up based on the displacement relative to the landing point. To control the landing point of the electrospinning jet, a target point may be set.

Low voltage, near field electrospinning has shown characteristics that differ from conventional near field electrospinning using higher voltage. Fiber diameter has already been shown to be smaller using this technique. With low voltage, near field electrospinning, the fiber diameter was found to be sensitive to the collector stage movement due to mechanical stretching; low velocity giving rise to larger fiber diameter and vice versa [Bisht et al 2011]. Instead of very fine spinneret tip, Bisht et al (2011) showed that it is possible to spin fibers with diameter less than 100 nm using a 27 gauge needle (approx. 200 \textmu m inner diameter).

\subsubsection{Electric field}Electrospinning jet can be very sensitive to variation in electric field. Thus a target with electric field profile that attracts the jet may be used to guide the electrospinning jet towards the desired landing point. Bisht et al (2011) demonstrated the precision and accuracy of low voltage, near field electrospinning by suspending fiber across carbon post with diameter of 30 \textmu m and interpostal distance of 100 \textmu m. Min et al (2013) used near field electrospinning to deposit semiconducting poly(3-hexylthiophene) (P3HT):PEO-blend organic nanowire over multiple field-effect transistors on a flexible polyarylate substrate at a speed of 13.3 cm/s with regular spacing of 50 \textmu m and fiber diameter of 289 nm. They have also demonstrated the ability to spin highly aligned nanowires from other materials such as poly(9-vinyl carbazole) (PVK) and poly\{[N,N'-bis(2-octyldodecyl)-naphthalene-1,4,5,8-bis(dicarboximide)-2,6-diyl]-alt-5,5'-(2,2'-bithiophene)\}.

The combination of near-field electrospinning and a guiding electrode has the potential to obtain precise and accurate fiber deposition. Xu et al (2014) used a guiding electrode behind the collector to create a direct line from the nozzle tip to it. This significantly dampens the deviation of the electrospinning jet from its original path as a result of electrostatic repulsion from the preceding deposited nano fiber. Without the guiding electrode, the near-field electrospun fibers have a spread of 74 \textmu m. With the guiding electrode, the spread was reduced to just 7 \textmu m. This raises the possibility of building up 3D structures using electrospinning. Kim et al (2018) used inkjet printing with conductive Ag nanoparticles loaded ink to form patterns on a paper as a target for near field electrospun fibers. The conductive printed pattern served as a guiding electrode for the electrospinning jet. Poly(vinylidene fluoride) (PVDF) solution was electrospun from a height of 750 \textmu m and a 150 \textmu m offset from the edge of the pattern. The sensitivity of the electrospinning jet towards the electric field can be seen as the fibers are stacked on the edge of the conductive pattern where the relative electric field was much higher at the edge than at its center. When the pattern lines formed acute angle, right-angle or obtuse angle, the accuracy of the deposited fibers are influenced by slight changes in the relative electric field. From acute angle to right-angle, the electric field singularity increases from the edge to the intersection between the lines. In this case, the fibers were stacked directly on the edge of the line and to the middle of the intersection. For lines forming obtuse angle, the deposited fibers followed the edge of the lines by veered off the line at the intersection.

\subsection{Substrate}In near field electrospinning, one of the risks is electrical shorting due to the proximity of the charged needle tip to the grounded collector. Any electrical shorting will disrupt the electrospinning process and result in discontinuous fiber. While using a lower voltage may reduce this risk, an alternative is to use a less conductive collector. Liu et al (2014) used a rotating glass tube with a copper foil lining at the inner surface of the tube for the collection of electrospun oriented polyvinylidene fluoride (PVDF) fiber. While initial fiber alignment was excellent, the alignment starts to deteriorate after prolonged fiber deposition which can be attributed to the presence of residual charges.

The influence of residual charges on the precision of fiber deposited is more pronounced when an insulating surface and a conductive surface were used as collectors. Choi et al (2017) used a hydrophobic and insulating acrylic substrate as collector. To increase conductivity of selected region of the collector, plasma treatment was carried out to render those region hydrophilic. The collector was placed in a high humidity environment such that the hydrophilic region will be slightly conductive due to the presence of water molecule attached to it. Near field electrospinning of polyurethane showed that on the insulating hydrophobic surface, the fibers were twisted and curved due to weak electric field profile between the emitter and the collector surface and the inability of charges to escape. In contrast, on the hydrophilic region, the fiber were placed in accordance to the movement of the emitter relative to the collector. This shows that electrical charges on the electrospinning jet needs to escape for precise deposition and even an insulating substrate with slight conductivity is crucial for ordered fiber arrangement.

\subsection{Polymer Solution}In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching. In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased [Chang et al 2008; Zheng et al 2012]. However, in separate studies by Pan et al (2014) using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and Pan et al (2015) using polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration. Pan et al (2015) attributed this to a higher charge accumulation in higher concentration PVDF solution. However, more studies need to be carried out to verify this.

\section{NFES Variants}
Low-Voltage NFES (LV NFES) \unskip~\cite{527120:11973130}

Scanning Tip Electrospinning \unskip~\cite{527120:11974306}

3D Electrospinning \unskip~\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\cite{527120:11974310}

Multinozzle NFES \unskip~\cite{527120:11974322,527120:11974323,527120:11974324}

Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\cite{527120:11974328} \mbox{}\protect\newline Mechano-Electrospinning \unskip~\cite{527120:11974304}

Suspension NFES \unskip~\cite{527120:12033656}

Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\cite{527120:11974320}

Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\cite{527120:11974312}

Tethered Pyro-Electrohydro-dynamic Spinning (TPES) \unskip~\cite{527120:11974307}

@@

Poly(ethylene oxide) (PEO; MW = 4,000,000) &

@@

Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV; MW = 380,000) with Poly(ethylene oxide) (PEO; MW = 300,000) &

@@

\section{Conclusion}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
